Title

### 2018-02-02 wfe/request/request-template.tex
rewritten ReQuEST CFP +  updated template

% LaTeX template for Artifact Evaluation V20170622
%
% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK),
% Bruce Childers (University of Pittsburgh, USA),
% Thierry Moreau (University of Washington, USA)
%
% See example of this Artifact Appendix in the CGO'17 paper (with the CK workflow framework):
% https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
%
% (C)opyright 2014-2017
%
% CC BY 4.0 license
%

@@

\begin{abstract}
Summary of work, and artifact.
\end{abstract}

@@

\subsection{Technical Description}
{\em Obligatory. Provide a technical desciption of your novel work, or references to
your already published work which you are providing an artifact for.}

@@

\appendix
\section{Artifact appendix}

Submission and reviewing guidelines and methodology: \\
{\em http://cTuning.org/ae/submission.html}

@@

{\small
\begin{itemize}
  \item {\bf Algorithm: }
  \item {\bf Program: }
  \item {\bf Compilation: }
  \item {\bf Transformations: }
  \item {\bf Binary: }
  \item {\bf Data set: }
  \item {\bf Run-time environment: }
  \item {\bf Hardware: }
  \item {\bf Run-time state: }
  \item {\bf Execution: }
  \item {\bf Metrics: }
  \item {\bf Output: }
  \item {\bf Experiments: }
  \item {\bf Workflow frameworks used?: }
  \item {\bf Publicly available?: }
\end{itemize}

{\em Obligatory. Provide brief assessment of your artifacts 
based on {\em https://www.acm.org/publications/policies/artifact-review-badging}}:

\begin{itemize}
  \item {\bf Artifacts publicly available?: }
  \item {\bf Artifacts functional?:}
  \item {\bf Artifacts reusable?:}
  \item {\bf Results validated?:}
\end{itemize}

@@

\subsubsection{How delivered}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% When adding this appendix to your paper, 
% please remove below part
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% LaTeX template for Artifact Evaluation V20180201
%
% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK)
% and Thierry Moreau (University of Washington, USA)
%
% This document was derived from the original Artifact Appendix
% prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK) 
% and Bruce Childers (University of Pittsburgh, USA)
%
% See example of this Artifact Appendix in the CGO'17 paper (with the CK workflow framework):
% https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
%
% (C)opyright 2014-2018
%
% CC BY 4.0 license
%

@@

\begin{abstract}
Summary of work and associated workflow artifact.

Please, specify if you want a public or a private evaluation.
\end{abstract}

@@

\subsection{Technical Description}
{\em Obligatory. Provide a technical description of your novel work, 
or references to your already published work which you are providing an artifact for.}

@@

\appendix
\section{Artifact Appendix}

Submission and reviewing methodology: \\
{\em http://cTuning.org/ae/submission-20171101.html}

@@

{\small
\begin{itemize}
  \item {\bf Algorithm: }
  \item {\bf Program: }
  \item {\bf Compilation: }
  \item {\bf Transformations: }
  \item {\bf Binary: }
  \item {\bf Data set: }
  \item {\bf Run-time environment: }
  \item {\bf Hardware: }
  \item {\bf Run-time state: }
  \item {\bf Execution: }
  \item {\bf Metrics: }
  \item {\bf Output: }
  \item {\bf Experiments: }
  \item {\bf Collective Knowledge workflow framework used?: } 
  \item {\bf Publicly available?: }
\end{itemize}

@@

\subsubsection{How to obtain?}

@@

Please, specify which metrics you improve
(execution time, accuracy, power consumption, 
memory usage, device cost, usage cost, etc)

@@
